The \frb\ Campaign: Multi-Observatory Radio Burst and Implications for the FRB Population

### 2017-03-22 repeater-vladata.tex
removing most simulation work. energy distribution figure looking good

The bottom panel of Figure \ref{fig:dmmodel} compares the DM to the modeled temporal width of the bursts. There is a weak correlation between burst width and apparent DM. A change in width of $\sim1$~ms correlates with a change in apparent DM of approximately $5$~pc cm$^{-3}$. If the excess DM is

@@

\subsection{Energy and Brightness Distribution}
\label{sec:disn}
Knowing the source distance, we calculate the burst energy by integrating flux in time and frequency (Table \ref{tab:spec}). Some VLA burst spectra seem to be contained by the 2.5 to 3.5~GHz band and most of them seem to have Gaussian envelopes that are well modeled by the emission within the 2.5 to 3.5~GHz band. Assuming that the Gaussian shape defines the emission window, the mean S-band flux density can be converted to a total energy with no further assumptions about their spectral properties. We proceed under this assumption here and discuss caveats in \S \ref{sec:disc}.

Figure \ref{fig:ed} shows the \frb\ burst energy cumulative distribution and best-fit model. We modeled the differential energy distribution, $dN/d\log{E}$, as a Poisson probability distribution with a rate function $\lambda\propto E^{\alpha}$. Using a maximum likelihood technique, we estimate the best powerlaw index of $\alpha=-0.6^{+0.2}_{-0.4}$ (68\% confidence interval), which is equivalent to a $dN/dE$\ powerlaw index of --1.6. This model assumes a completeness limit for a luminosity equivalent to an $8\sigma$\ flux density limit, which is consistent with the high and uniform data quality.

\begin{figure}[htb]
\begin{center}
\includegraphics[width=0.9\columnwidth]{energy_disn}
\caption{Dots and solid line show the  \frb\ burst energy cumulative distribution. The dashed line shows the best fit from a maximum likelihood analysis using the powerlaw model $dN/d\log{E} \propto E^{\alpha}$. The 95\% bounds on the best-fit powerlaw index is $\alpha=-0.6^{+0.2}_{-0.4}$. \label{fig:ed}}
\end{center}
\end{figure}

@@

\subsection{Energy and Flux Distribution}
The refined analysis shows that \frb\ has even higher isotropic energies than previously reported, reaching energies $E_{\rm{max}}\approx10^{40}$\ erg. We now know that \frb\ is detectable with the VLA out to $z=0.7$\ and much farther with Arecibo. \frb\ has isotropic energies orders of magnitude higher than the strongest Crab pulsar pulses ($\sim10^{35}$~erg) and comparable brightness temperatures \citep[$T_b^{\rm{Crab}}\sim10^{41}$~K versus $T_b^{\rm{FRB 121102}}\sim10^{38}$~K;][]{2003Natur.422..141H,2014PhRvD..89j3009K}. While this emission is coherent and strongly beamed \citep{2016Natur.531..202S, WEIRD}, the energy scale is still larger than any known Galactic radio transient and requires either a new process or dramatic scaling of known emission processes \citep{2016MNRAS.462..941L, 2016MNRAS.457..232C}.

The nine bursts were detected with a wide range of significance (12 to 179$\sigma$) and the apparent burst energy distribution can be characterized as a powerlaw $dN/dE\propto E^{-1.6}$. With only 9 VLA bursts, it is difficult to draw strong inferences, but a similar energy index has been observed in X-ray fluxes of solar flares \citep{2011SoPh..274...99A} and gamma-ray fluence for soft-gamma repeaters \citep{2000ApJ...532L.121G, 2011ApJ...739...94S}. This distribution is similar to that seen in earthquakes and other phenomena generally termed ''self-organized criticality'' \citep{2011SoPh..274...99A}.

FRB detections have often been far brighter than the limiting brightness of telescopes detecting them \citep{2007Sci...318..777L, 2016arXiv161105758R}. This perception has been supported by analysis that suggests that the cumulative flux distribution ($dN/dF \propto F^{\alpha}$) is relatively flat \citep[$-0.5<\alpha<-0.9$;][]{2016ApJ...830...75V, 2016arXiv160206099L, 2016arXiv161100458L}. For a uniform distribution of sources, we expect a ''Euclidean distribution'' with $\alpha=-1.5$ \citep{2016MNRAS.462..941L}.
V/Vmax
If all FRBs luminosities are drawn from such a distribution, then their flux distribution will be determined by the underlying energy distribution and its interplay with redshift space distortions.

We tested this idea by simulating FRB populations and measuring the properties of a flux-limited sub-sample. First, we assume an FRB population that is uniformly distributed in space from redshifts $z1$\ to $z2$. For each FRB source, we generate one FRB burst with a luminosity drawn from the \frb\ energy distribution and calculate its flux. We then select the brightest 15 \citep[equal to the current sample size used in modeling;][]{2016ApJ...830...75V} and fit a powerlaw to the $dN/dF$\ distribution. Typically, a large ($N>10000$) population of such bursts is needed to avoid edge effects in the properties of the flux-limited subsample.

Figure \ref{fig:sim} shows an example of an FRB population simulation with a $dN/dE$\ distribution like \frb. We use visualizations like this to verify that the simulations are not affected by edge effects. We can also reproduce a Euclidean flux distribution for a standard candle-like luminosity distribution at low redshift and that distributions out to $z2\sim2$ have a flatter index ($\Delta\alpha\sim0.2$) due to redshift space distortions.

\begin{figure*}[htb]
\begin{center}
\includegraphics[width=1.8\columnwidth]{sim_L1.6}
\caption{An example of a simulated FRB population. (Top left) The input luminosity distribution, which follows the \frb\ distribution of $dN/dE\propto E^{-1.6}$. (Top right) The input redshift space distribution of a uniform distribution of FRB sources. (Bottom left) The measured flux distribution of the simulation with red lines showing fits to the whole population and brightest 15 FRBs. (Bottom right) The flux-redshift distribution of the simulated population. The dahsed line shows the limiting flux that includes the brightest 15 sources.
\label{fig:sim}}
\end{center}
\end{figure*}

To study how the input parameters affect the measured flux distribution, so we generated 100 populations to measure 68\% confidence intervals on the cumulative flux distribution index. Figure \ref{fig:ind} shows the result of several such measurements for input luminosity distribution index ranging from --2.2 to --1.2. Generally, the measured flux distribution index flattens as the input luminosity distributions flattens. The best constraint on the flux distribution index \citep{2016ApJ...830...75V} requires an input energy distribution index between roughly --2.1 and --1.4, which is consistent with the measured energy distribution for \frb. These simulations predict a mean a mean redshift between 0.9 and 1.8, which is in weak tension with the mean FRB redshift inferred from DM. For a mean total DM of $750$\ pc cm$^{-3}$ and a mean host DM of 200 pc cm$^{-3}$, we expect a mean redshift of $\sim0.6$ \citep[$z=DM/900$\ pc cm$^{-3}$;][]{2004MNRAS.348..999I}.

\begin{figure}[htb]
\begin{center}
\includegraphics[width=0.9\columnwidth]{sim_index_scaling}
\caption{Scaling of apparent flux distribution index for given luminosity (or energy) distribution index.
\label{fig:ind}}
\end{center}
\end{figure}

While the \frb\ burst energy distribution is consistent with the overall FRB population, this simulation ignores many observational biases (scattering, observing coverage) and the effects of galaxy evolution, which is likely significant over the range of redshifts to which \frb is detectable \citep[e.g.,][]{2010ApJ...709..644I}. The burst energies are estimated from observations from 2.5 to 3.5~GHz, which may be a biased selection of all bursts or may not include all burst emission. If the simulation is revealing a connection between \frb and the broader FRB population, it does not explain the physical mechanism that drives it. The burst energy distribution of the population could be dominated by intrinsic or extrinsic effects \citep{2015MNRAS.451.3278M,2016Natur.531..202S,CORDES}. More FRB detections will improve the quality of this inference as sample variance drops, while more burst detetions from \frb\ will improve the measurement of the intrinsic energy distribution.

@@

\section*{Acknowledgements}
% observatories
The National Radio Astronomy Observatory is a facility of the National Science Foundation operated under cooperative agreement by Associated Universities, Inc..
% systems
This research made use of Astropy, a community-developed core Python package for Astronomy (Astropy Collaboration, 2013).
%individuals
CJL is supported by the University of California Office of the President under Lab Fees Research Program Award 237863 and NSF award **number**.
MAM is supported by NSF award \#1458952. 
KPM's research is supported by the Oxford Centre for Astrophysical Surveys which is funded through the Hintze Family Charitable Foundation. AS gratefully acknowledges support from the European Research Council under grant ERC-2012- StG-307215 LODESTONE. The AMI-LA telescope gratefully acknowledges support from the European Research Council under grant ERC-2012- StG-307215 LODESTONE, the UK Science and Technology Facilities Council (STFC) and the University of Cambridge.

>>>>

The bottom panel of Figure \ref{fig:dmmodel} compares the DM to the modeled temporal width of the bursts. There is a weak correlation between burst width and apparent DM. A change in width of $\sim1$~ms correlates with a change in apparent DM of approximately $5$~pc cm$^{-3}$.

@@

\subsection{Energy and Brightness Distribution}
\label{sec:disn}
Knowing the source distance, we calculate the burst energy by integrating flux in time and frequency (Table \ref{tab:spec}). Some VLA burst spectra seem to be contained by the 2.5 to 3.5~GHz band and most of them seem to have Gaussian envelopes that are well modeled by the emission within that band. Assuming that the Gaussian shape defines the emission window, the mean S-band flux density can be converted to a total energy with no further assumptions about their spectral properties.

Figure \ref{fig:ed} shows the \frb\ burst energy cumulative distribution as seen by the VLA and calculated from prior observations by Arecibo and the GBT \citep{2016Natur.531..202S,2016arXiv160308880S}. The latter two energy distributions are scaled from the fluence by assuming that all burst energy is included by the observation. This likely underestimates the burst energy for some bursts by a factor of a few, but should not affect the slope of the distribution. The Arecibo and GBT energies were scaled by factors of {\color{red} 2 and 1 (help)}, respectively, to correct for the sensitivity loss due to the primary beam.

Broadly, the range of energies shown in Figure \ref{fig:ed} is defined by the sensitivity of the telescope and the duration of the observing campaign. The VLA distribution shown represents the 27-hour, late-2016 campaign, which is longer than the single-dish campaigns presented here. However, since the VLA observations have a relatively coarse time resolution, it is not as sensitive as Arecibo and the GBT, so no bursts were detected weaker than $3\times10^{38}$~erg. The rate upper limit (95\% confidence) from the early-2016 VLA campaign shows that even identical observing campaigns have different detection rates.

We modeled the differential energy distribution, $dN/d\log{E}$, using a Poisson probability distribution with a rate function $\lambda = A E^{\alpha}$. Rather than trying to estimate a completeness limit for each energy distribution, we assume an effective detection limit of 0.9 times the weakest burst detected; the best-fit slope is weakly dependent on this, but general conclusions are robust. We directly sampled the likelihood distribution to estimate a best slope of $\alpha_{\rm{VLA}}=-0.7^{+0.3}_{-0.4}$, $\alpha_{\rm{AO}}=-0.8^{+0.3}_{-0.5}$, and $\alpha_{\rm{GBT}}=-0.8^{+0.4}_{-0.5}$ (68\% confidence interval). Expressed as a powerlaw function in $dN/dE$, the slope index is approximately --1.7.

\begin{figure}[htb]
\begin{center}
\includegraphics[width=0.9\columnwidth]{energy_disn}
\caption{The cumulative burst energy distributions for the VLA, Arecibo, and GBT are shown with dots connected by solid, dashed, and dotted lines, respectively. The Arecibo distribution is derived from the 11 1.4~GHz bursts reported in \citet{2016Natur.531..202S} and the GBT distribution is derived from the 5 1.4~GHz bursts reported in \citet{2016arXiv160308880S}. An upper limit from the VLA nondetection in early 2016 is shown as a triangle. \label{fig:ed}}
\end{center}
\end{figure}

@@

\subsection{Energy and Flux Distribution}
The refined analysis shows that \frb\ has even higher isotropic energies than previously reported, reaching energies $E_{\rm{max}}\approx10^{40}$\ erg. We now know that \frb\ is detectable with the VLA out to $z=0.7$. \frb\ has isotropic energies orders of magnitude higher than the strongest Crab pulsar pulses ($\sim10^{35}$~erg) and comparable brightness temperatures \citep[$T_b^{\rm{Crab}}\sim10^{41}$~K versus $T_b^{\rm{FRB 121102}}\sim10^{38}$~K;][]{2003Natur.422..141H,2014PhRvD..89j3009K}. While this emission is coherent and strongly beamed \citep{2016Natur.531..202S, WEIRD}, the energy scale is still larger than any known Galactic radio transient and requires either a new process or dramatic scaling of known emission processes \citep{2016MNRAS.462..941L, 2016MNRAS.457..232C}.

In \S \ref{sec:disn} we compare the energy distribution of the 9 VLA bursts to those reported earlier by Arecibo and the GBT. In all cases, bursts are detected over a wide range of significance that is indicative of a relatively flat distribution. All three energy distributions can be characterized as a powerlaw in $dN/dE$ with slope $\sim-1.7$. This slope is seen even though the burst rate varies by almost an order of magnitude between observations and frequencies cover both 1.4 and 3~GHz bands. This suggests that the slope is related to the underlying physical process, rather than the state at any given time. The value of the energy distribution slope is similar to that observed in X-ray fluxes of solar flares \citep{2011SoPh..274...99A} and gamma-ray fluence of bursts from soft-gamma repeaters \citep{2000ApJ...532L.121G, 2011ApJ...739...94S}. In these cases, the value of the slope is close to the theoretical expectation for self-regulated critical phenomena \citep[slope$=-5/3$;][]{2011SoPh..274...99A}.

This work expands the redshift horizon for detectability of \frb, suggesting that cosmological effects are even more important for understanding properites of the FRB population. An early observable property of the FRB population is the flux distribution, $dN/dF \propto F^{\alpha}$. For a uniform distribution of sources, the powerlaw index, $\alpha$, takes on the special value of --1.5 \citep[the ''Euclidean distribution'';][]{2016MNRAS.462..941L}. Deviations from the Euclidean distribution have been used to suggest that GRBs were indeed a cosmological distribution. Multiple studies have suggested that FRBs have a ''flat'' flux distribution \citep[$-0.5<\alpha<-0.9$;][]{2016ApJ...830...75V, 2016arXiv160206099L, 2016arXiv161100458L}, although others have cautioned that a powerlaw distribution is an approximation that can confuse any meaningful inferences \citep{2017arXiv170208040C}.

\citet{2017arXiv170208040C} describe show how the measured flux distribution is sensitive to the maximum distance...
FRB detections have often been far brighter than the limiting brightness of telescopes detecting them \citep{2007Sci...318..777L, 2016arXiv161105758R}. 
This is well known in the study of GRBs, which used the $V/V_{\rm{max}}$\ test (ratio of maximum to limiting brightness) to first infer that that population was cosmological \citep{1992ApJ...388L..45M}.

Effects relevant to FRBs:
- redshift space distortion
- time dilation (rate calculation correction scales as $1+z$)
- frequency-dependent FRB rate
All tend to flatten the $dN/dF$\ distribution with increasing z.

The VLA and Arecibo observed intensively during the late-2016 campaign, but a complete search for bursts from the Arecibo is ongoing. Soon we will be able to calculate a frequency-dependent burst rate, but early results suggest that the burst rate at a fixed energy is much higher at 1.4~GHz than at 3~GHz. If so, we should expect an additional redshift-dependent effect that will flatten the $dN/dF$\ distribution.

%While the \frb\ burst energy distribution is consistent with the overall FRB population, this simulation ignores many observational biases (scattering, observing coverage) and the effects of galaxy evolution, which is likely significant over the range of redshifts to which \frb is detectable \citep[e.g.,][]{2010ApJ...709..644I}. The burst energies are estimated from observations from 2.5 to 3.5~GHz, which may be a biased selection of all bursts or may not include all burst emission. If the simulation is revealing a connection between \frb and the broader FRB population, it does not explain the physical mechanism that drives it. The burst energy distribution of the population could be dominated by intrinsic or extrinsic effects \citep{2015MNRAS.451.3278M,2016Natur.531..202S,CORDES}. More FRB detections will improve the quality of this inference as sample variance drops, while more burst detetions from \frb\ will improve the measurement of the intrinsic energy distribution.

@@

\section*{Acknowledgements}
% observatories
The National Radio Astronomy Observatory is a facility of the National Science Foundation operated under cooperative agreement by Associated Universities, Inc..
% systems
This research made use of Astropy, a community-developed core Python package for Astronomy (Astropy Collaboration, 2013).
%individuals
CJL is supported by the University of California Office of the President under Lab Fees Research Program Award 237863 and NSF award **number**.
MAM is supported by NSF award \#1458952. 
KPM's research is supported by the Oxford Centre for Astrophysical Surveys which is funded through the Hintze Family Charitable Foundation. AS gratefully acknowledges support from the European Research Council under grant ERC-2012- StG-307215 LODESTONE. The AMI-LA telescope gratefully acknowledges support from the European Research Council under grant ERC-2012- StG-307215 LODESTONE, the UK Science and Technology Facilities Council (STFC) and the University of Cambridge.
We acknowledge...
Aspen Center for Physics
Liam Connor
